Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
aws index

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{AWS Instances}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances}
\label{table:iperf}
\tabcolsep=0.4cm
\begin{center}\begin{tabular}{ccc}
Server & Client & BandWidth Gb/s\\ \hline \hline
g2.8xlarge & c3.2xlarge & 1 \\ \hline
g2.8xlarge & c3.8xlarge & 7.5 \\ \hline
g2.8xlarge & g2.2xlarge & 1 \\ \hline
g2.8xlarge & g2.8xlarge & 7.5 \\ \hline
\end{tabular}\end{center}\end{table}

\section{Working with Remote GPUs in AWS}
\label{sec:rgpuaws}

@@

\begin{itemize}
\item Escenarios creados
\item Experimentos
\item An\'alisis basados en flexibilidad y coste econ\'omico
\end{itemize}

>>>>

\section{Working with AWS}
\label{sec:aws}

\subsection{Current Features}

\subsubsection{Instances}
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{AWS Instances}
\label{table:awsInstances}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccccc}
Name & vCPUs & Memory & Network & GPUs & Price\\ \hline \hline
c3.2xlarge & 8 & 15 GiB & High & 0 & \$ 0.21\\ \hline
c3.8xlarge & 32 & 60 GiB & 10 Gb & 0 & \$ 1.68 \\ \hline
g2.2xlarge & 8 & 15 GiB & High & 1 & \$ 0.65\\ \hline
g2.8xlarge & 32 & 60 GiB & 10 Gb & 4 & \$ 2.6 \\ \hline
\end{tabular}\end{center}\end{table}

\subsubsection{Network}
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{IPERF results between instances}
\label{table:iperf}
\tabcolsep=0.24cm
\begin{center}\begin{tabular}{cccc}
Server & Client & Network & BandWidth\\ \hline \hline
g2.8xlarge & c3.2xlarge & High & 1  Gb/s\\ \hline
g2.8xlarge & c3.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
g2.8xlarge & g2.2xlarge & High & 1 Gb/s\\ \hline
g2.8xlarge & g2.8xlarge & 10Gb & 7.5  Gb/s\\ \hline
\end{tabular}\end{center}\end{table}

\subsubsection{GPUs}

@@

\subsection{Testbed Scenarios}
\subsection{Experiments}
\subsection{Results}
Flexibility and economical expenses
